Predicting tree failure likelihood for utility risk mitigation via artificial intelligence

### 2021-03-03 docs/manuscript/manuscript.tex
man updates
Updates from Overleaf

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{raw_input_images_2}
  \caption{Random examples of the raw training images (2 are shown per class). Images are antialiased in this figure for greater clarity.}
  \label{fig:raw_images}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=1.05\textwidth]{scenario_resolution_performance.png}
    \caption{Performance metrics for each scenario and input resolution instance. Average metrics and 95\% confidence intervals (trials, $n=5) are shown for 10 epochs in each case.}
    \label{fig:sens-overall}
\end{figure}

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{Labeled example trees.png}
  \caption{Examples of the raw training images (2 are shown per class).  Trees in the left column were categorized as improbable due to their lack of structural defects as well as good physiological health.  Trees in the center column were categorized as possible due to weak branch unions and dieback of crown extremities.  Trees in the right column were categorized as probable for extensive sections of dead wood in the upper photograph, and a standing dead tree in the lower photograph. Images are antialiased in this figure for greater clarity.}
  \label{fig:raw_images}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=1.05\textwidth]{scenario_resolution_performance.png}
    \caption{Performance metrics for each scenario and input resolution instance. Average metrics and 95\% confidence intervals (trials, $n=5$) are shown for 10 epochs in each case.}
    \label{fig:sens-overall}
\end{figure}
